More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-07-18 2016-Weak-FH-Bisim/WeakBisim.tex
adding lemma
un peu de reorga et de redaction

\section{Notations}

\subsubsection{Syntax and Notations}
\TODO{copy pasted -- rearrange + move?}

In the following definitions, we extensively use indexed structures
(maps) over some countable indexed sets. The indices will usually be
integers, bounded or not. Such an indexed family is denoted as
follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the
set $I$. Such a family
is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$, and we will also use mapping 
notations to manipulate indexed sets.
To specify the set over which the structure is indexed, 
indexed structures are always denoted with an exponent of the form $i\in I$
(arithmetic only appears in the indexes if necessary).
Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
family is indexed, and then $a_i$ the elements of the family.

@@

\section{Parameterised Networks (pNets): definition}
\label{section:pnets}

@@

\def\Talg{\mathcal{T}_{\Sigma,\P}}
\def\BoolExprs{\mathcal{B}_{\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of boolean
expressions $\BoolExprs$ ($\BoolExprs\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
naturally action terms will use data expressions as subterms.
To be able to reason about the data flow between pLTSs, we
distinguish \emph{input variables} of the form $?x$ within terms; the function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns its input variables.
Action algebras can encode naturally usual point-to-point message passing calculi (using 
$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
for more general mechanisms, like gate negociation in Lotos, or broadcast
communications.

\subsection{The (open) pNets Core Model}
\label{section:pNets}

@@

We first define the set of actions a pLTS can use, let $a$
range over action labels, $\symb{op}$ are operators, and $x_i$ range over
variable names. Action terms of \pLTS s are:
\[
\begin{array}[l]{rcl@{\quad}p{5.5cm}}
  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
\end{array}
\]
The input variables in an action term are those marked with a
$\symb{?}$.
We additionally suppose that each input variable does not
appear somewhere else in the same action term:
$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$

@@

A composite pNet consists of a set of sub-pNets exposing
a set of actions, each of them synchronising actions in each of
the sub-pNets. The synchronisation between global actions and
internal actions is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.
Actions involved at the pNet level (in the synchronisation vectors) do
not need to distinguish  input 
variables. Action terms used in synchronisation vectors of pNets are defined as follows:
\[\begin{array}[l]{rcl@{\quad}l}
  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
\end{array}
\]

@@

\TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}

>>>>

\section{Background and notations}
This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
\subsubsection{Syntax and Notations}

In the following definitions, we extensively use indexed structures
(maps) over some countable indexed sets.   The indices will usually be
integers, bounded or not. We use indexed sets in pNets because we want to consider a set of processes, and provide an additional structure that explains how to synchronise them. Basically this could be done by tuples (but not by sets), however indexed sets are more general, can be infinite, and give a compact representation (the position is easier to express).

An indexed family is denoted as
follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the
set $I$. Such a family
is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$, and we will also use mapping 
notations to manipulate indexed sets.
To specify the set over which the structure is indexed, 
indexed structures are always denoted with an exponent of the form $i\in I$.
Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
family is indexed, and then $a_i$ the elements of the family.

@@

\def\Talg{\mathcal{T}_{\Sigma,\P}}
\def\BoolExprs{\mathcal{B}_{\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of boolean
expressions $\BoolExprs$ ($\BoolExprs\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
naturally action terms will use data expressions as subterms.

We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. Let $a$
range over action labels, $\symb{op}$ be operators, and $x_i$ range over
variable names.

We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
\[
\begin{array}[l]{rcl@{\quad}p{5.5cm}}
  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
\end{array}
\]
The \emph{input variables} in an action term are those marked with a
$\symb{?}$.
We additionally suppose that each input variable does not
appear somewhere else in the same action term:
$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$

We first define the set of actions that do not distinguish input variables, they will be used in synchronisation vectors of pNets below:
\[\begin{array}[l]{rcl@{\quad}l}
  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
\end{array}
\]

The function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns its input variables.
Action algebras can encode naturally usual point-to-point message passing calculi (using 
$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
communications.

\subsection{Parameterised Networks (pNets): definition}
\label{section:pnets}

@@

@@

@@

A composite pNet consists of a set of sub-pNets exposing
a set of actions, each of them synchronising actions in each of
the sub-pNets. The synchronisation between global actions and
internal actions is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.

@@

\TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}
\begin{lemma}
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
If $A_1$ and $A_2$ are weak FH-bisimilar then 
\begin{itemize}
 \item  For any weak open transition $wOT_1$ in $WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT_1},\Post_{OT_1}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
 there exists weak open transition $wOT_2$ in $WT_2$ :
 \begin{mathpar}
    \openrule
         {
           {\gamma\,'}_{j}^{j\in J_2}, \Pred_{OT_2},\Post_{OT_2}}
         {t \OTWeakarrow {\alpha} t'}
\end{mathpar}
 such that  $J_1=J_{2}, (s'\!,t'|\Pred_{s',t'})\in \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT_1}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_1. \gamma_j=\gamma'_{j}  \Rightarrow \Pred_{OT_2}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s'\!,t'}\subst{\Post_{OT_1}}\subst{\Post_{OT_2}}\right)$

\end{itemize}
\end{lemma}
